\begin{filecontents}{T12-related-work.bib}
@INPROCEEDINGS{ChildersChrysanthis2017,
  author={Childers, Bruce R. and Chrysanthis, Panos K.},
  booktitle={IEEE 13th International Conference on e-Science (e-Science)}, 
  title={{Artifact Evaluation: Is It a Real Incentive?}}, 
  year={2017},
  pages={488-489},
  doi={https://doi.org/10.1109/eScience.2017.79}
}

@INPROCEEDINGS{ChildersChrysanthis2018,  
    author={Childers, Bruce R. and Chrysanthis, Panos K.}, 
    booktitle={IEEE 34th International Conference on Data Engineering (ICDE)},   
    title={{Artifact Evaluation: FAD or Real News?}},   
    year={2018},  
    pages={1664-1665},  
    doi={https://doi.org/10.1109/ICDE.2018.00204}
}

@inproceedings{HermannWinterSiegmund2020,
author = {Hermann, Ben and Winter, Stefan and Siegmund, Janet},
title = {{Community Expectations for Research Artifacts and Evaluation Processes}},
year = {2020},
isbn = {9781450370431},
booktitle = {Proceedings of the 28th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering},
publisher = {ACM},
doi = {https://doi.org/10.1145/3368089.3409767},
pages = {469–480},
numpages = {12},
location = {Virtual Event, USA},
series = {ESEC/FSE 2020}
}

@article{HeumullerEtAl2020,
author = {Heum\"{u}ller, Robert and Nielebock, Sebastian and Kr\"{u}ger, Jacob and Ortmeier, Frank},
title = {{Publish or Perish, but Do Not Forget Your Software Artifacts}},
year = {2020},
publisher = {Kluwer Academic Publishers},
doi = {https://doi.org/10.1007/s10664-020-09851-6},
journal = {Empirical Software Engineering},
}

@inproceedings{WacharamanothamEtAl2020,
    author = {Wacharamanotham, Chat and Eisenring, Lukas and Haroz, Steve and Echtler, Florian},
    title = {{Transparency of CHI Research Artifacts: Results of a Self-Reported Survey}},
    year = {2020},
    isbn = {9781450367080},
    publisher = {ACM},
    doi = {https://doi.org/10.1145/3313831.3376448},
    booktitle = {Proceedings of the 2020 CHI Conference on Human Factors in Computing Systems},
    pages = {1–14},
    numpages = {14},
    location = {Honolulu, HI, USA},
    series = {CHI '20}
}

@article{TimperleyEtAl2021,
    author = {Timperley, Christopher S. and Herckis, Lauren and Le Goues, Claire and Hilton, Michael},
    title = {{Understanding and Improving Artifact Sharing in Software Engineering Research}},
    year = {2021},
    issue_date = {Jul 2021},
    publisher = {Kluwer Academic Publishers},
    address = {USA},
    volume = {26},
    number = {4},
    ISSN = {1382-3256},
    doi = {https://doi.org/10.1007/s10664-021-09973-5},
    journal = {Empirical Software Engineering},
    month = {07},
    numpages = {41}
}

@inproceedings{WinterEtAl2022,
    author = {Winter, Stefan and Timperley, Christopher S. and Hermann, Ben and Cito, J\"{u}rgen and Bell, Jonathan and Hilton, Michael and Beyer, Dirk},
    title = {{A Retrospective Study of One Decade of Artifact Evaluations}},
    year = {2022},
    doi = {https://doi.org/10.1145/3540250.3549172},
    booktitle = {Proceedings of the 30th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering},
    series = {ESEC/FSE 2022}
}

@article{Frachtenberg2022,
     title = {Research artifacts and citations in computer systems papers},
     author = {Frachtenberg, Eitan},
     year = 2022,
     month = feb,
     volume = 8,
     pages = {e887},
     journal = {PeerJ Computer Science},
     issn = {2376-5992},
     doi = {https://doi.org/10.7717/peerj-cs.887}   
}

@INPROCEEDINGS{AhmedOrtizEisty2024,
  author={Ahmed, Sharif and Ortiz, Rey and Eisty, Nasir U.},
  booktitle={IEEE/ACIS 22nd International Conference on Software Engineering Research, Management and Applications (SERA)}, 
  title={{Decade-long Utilization Patterns of ICSE Technical Papers and Associated Artifacts}}, 
  year={2024},
  doi={https://doi.org/10.1109/SERA61261.2024.10685638}
}

@article{GuevaraVegaEtAl2024,
title = {{Research artifacts for human-oriented experiments in software engineering: An ACM badges-driven structure proposal}},
journal = {Journal of Systems and Software},
volume = {218},
pages = {112187},
year = {2024},
issn = {0164-1212},
doi = {https://doi.org/10.1016/j.jss.2024.112187},
author = {Cathy Guevara-Vega and Beatriz Bernárdez and Margarita Cruz and Amador Durán and Antonio Ruiz-Cortés and Martin Solari},
}

@inproceedings{GuilloteauEtAl2024,
author = {Guilloteau, Quentin and Ciorba, Florina and Poquet, Millian and Goepp, Dorian and Richard, Olivier},
title = {{Longevity of Artifacts in Leading Parallel and Distributed Systems Conferences: a Review of the State of the Practice in 2023}},
year = {2024},
isbn = {9798400705304},
publisher = {ACM},
doi = {https://doi.org/10.1145/3641525.3663631},
booktitle = {Proceedings of the 2nd ACM Conference on Reproducibility and Replicability},
pages = {121–133},
numpages = {13},
location = {Rennes, France},
series = {ACM REP '24}
}

@article{LiuEtAl2024,
title = {Research artifacts in software engineering publications: Status and trends},
journal = {Journal of Systems and Software},
year = {2024},
doi = {https://doi.org/10.1016/j.jss.2024.112032},
author = {Mugeng Liu and Xiaolong Huang and Wei He and Yibing Xie and Jie M. Zhang and Xiang Jing and Zhenpeng Chen and Yun Ma},
}
\end{filecontents}

\documentclass{article}

%%% Packages
\usepackage[margin=1.8cm]{geometry}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage[table]{xcolor}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{pdflscape}
\usepackage{natbib}
\usepackage{xspace}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%
%% Table 12
%%%%%%%%%%%%%%%%%%%%%%%%

\setcounter{table}{11}%Table 12

\begin{landscape}
\scriptsize
\begin{longtable}{@{} p{24mm} p{40mm} p{29mm} p{30mm} p{30mm} p{38mm} p{28mm} @{}}
\caption{Related work.}
\label{tab:related-work}\\

\toprule
\multirow{3}{*}{\textbf{Work}} &
\multirow{3}{*}{\textbf{Data source}} &
\multirow{3}{*}{\textbf{RQ1:~Artifact calling}} &
\multirow{3}{*}{\textbf{RQ2:~Artifact sharing}} &
\textbf{RQ3:~Non-publicly-disclosure statements} &
\textbf{RQ4:~Artifact calling influence} &
\textbf{RQ5:~Artifact sharing and evaluation relationship} \\ 
\midrule
\endfirsthead

\toprule
\multirow{3}{*}{\textbf{Work}} &
\multirow{3}{*}{\textbf{Data source}} &
\multirow{3}{*}{\textbf{RQ1:~Artifact calling}} &
\multirow{3}{*}{\textbf{RQ2:~Artifact sharing}} &
\textbf{RQ3:~Non-publicly-disclosure statements} &
\textbf{RQ4:~Artifact calling influence} &
\textbf{RQ5:~Artifact sharing and evaluation relationship} \\ 
\midrule
\endhead


Childers and Chrysanthis (\citeyear{ChildersChrysanthis2017,ChildersChrysanthis2018}) &
Papers from three Programming Language conferences with the Artifact Evaluation process (ECOOP, OOPSLA, and PLDI) published from 2013 to 2016. &
\makecell[c]{\multirow{6}{*}{--}} &
\makecell[c]{\multirow{6}{*}{--}} &
\makecell[c]{\multirow{6}{*}{--}} &
\makecell[c]{\multirow{6}{*}{--}} &
%-- &
Correlation between successful artifact evaluation and paper citation.\\
\midrule



\cite{HermannWinterSiegmund2020} & 
Survey among 257 members of AE Committees and analysis of the CfA of Software Engineering and Programming Language venues (including ICSE and FSE) from 2011 to 2019. &
CfAs and artifact review guidelines instead of artifact calling over time. &
\makecell[c]{\multirow{6}{*}{--}} &
\makecell[c]{\multirow{6}{*}{--}} &
\makecell[c]{\multirow{6}{*}{--}} &
%-- &
\makecell[c]{\multirow{6}{*}{--}} \\
\midrule



\cite{HeumullerEtAl2020} &
ICSE research track papers (789) published from 2007 to 2017 (editions with no active Open Science initiatives). Focused on Software Artifact Papers, excluding papers with other artifact types. &
Artifact publishing guidelines instead of artifact calling over time. &
Less comprehensive scope (only software as artifact, only ICSE papers) and no recent temporal coverage. &
\makecell[c]{\multirow{6}{*}{--}} &
Different goal (evolution analysis only, not artifact calling influence); less comprehensive scope (only software as artifact, only ICSE papers) and no recent temporal coverage. &
%-- &
Correlation between linking to artifacts in a paper and paper citation. \\
\midrule



\cite{WacharamanothamEtAl2020} &
Survey among 460 first authors of papers from CHI 2018 and 2019. &
\makecell[c]{\multirow{4}{*}{--}} &
Different research community, limited and no recent temporal coverage (two years only). &
Reasons for non-disclosure based on survey responses instead of statements in papers. &
\makecell[c]{\multirow{4}{*}{--}} &
%-- &
\makecell[c]{\multirow{4}{*}{--}} \\
\midrule



\cite{TimperleyEtAl2021} &
Technical track papers (1,434) published at ICSE, FSE, ASE, and EMSE, from 2014 to 2018, and survey among 153 authors of the papers published in 2018. &
\makecell[c]{\multirow{6}{*}{--}} &
More conferences but less comprehensive and no recent temporal coverage (no coverage of ICSE editions with active Open Science policies).
&
Reasons for non-disclosure based on survey responses instead of statements in papers. &
Different goal (evolution analysis only, not artifact calling influence); more conferences but less comprehensive and no recent temporal coverage (no coverage of ICSE editions with active Open Science initiatives). &
%-- &
\makecell[c]{\multirow{6}{*}{--}} \\
\midrule






\cite{WinterEtAl2022} &
Papers (3,650) from 12 conferences, focusing on years that included Artifact Evaluation tracks. Included two years of ICSE (2019 and 2020) and nine non-consecutive years of FSE (between 2011 and 2020). &
-- &
More conferences but less comprehensive and no recent temporal coverage (no coverage of ICSE editions with active Open Science policies). &
-- &
Different goal (evolution analysis only, not artifact calling influence); more conferences but less comprehensive and no recent temporal coverage (no coverage of ICSE editions with active Open Science policies). &
%-- &
Relationships between papers with artifacts and citation, and how evaluated and not evaluated artifacts differ with respect to quality criteria. \\

\midrule


\cite{Frachtenberg2022} &
Papers (2,439) from 56 Systems and related conferences published in 2017. &
-- &
Different research community and limited temporal coverage (only one year). &
-- &
-- &
%-- &
Relationships between different artifact properties and paper citation. \\
\midrule

\cite{AhmedOrtizEisty2024} &
ICSE technical track papers (234) that included artifacts published in 2011 to 2021. &
-- &
Different scope (only papers with artifacts) and no recent temporal coverage. &
-- &
Different goal (evolution analysis only, not artifact calling influence); different scope (papers with artifacts only) and no recent temporal coverage. &
%-- &
Correlations between artifact attributes and platform attributes.\\
\midrule



\cite{GuevaraVegaEtAl2024} &
Papers (267) from the journals TSE, EMSE, JSS, and IST, from 2000 to 2022, and their guidelines. Focused on Human-Oriented Experiments in Software Engineering. &
Journal guidelines to research artifacts instead of artifact calling. &
Narrowed scope (papers with Human-Oriented Experiments only). &
-- &
Artifact compliance with journal guidelines, but narrowed scope (papers with Human-Oriented Experiments only). &
-- \\
\midrule



\cite{GuilloteauEtAl2024} &
Papers (296) from five conferences on Parallel and Distributed Systems (CCGrid, EuroSys, OSDI, PPoPP, and SC) published in 2023. &
-- & 
Different research community and limited temporal coverage (only one year). &
-- &
-- &
%-- &
-- \\
\midrule



\cite{LiuEtAl2024} &
Papers (2,196) from the research track of ICSE, FSE, ASE, and ISSTA, from 2017 to 2022. &
-- &
More conferences but less comprehensive temporal coverage (almost half of ours). &
-- &
Only some practices (e.g., URL location in papers) are discussed in the context of policies; more conferences but less comprehensive temporal coverage (almost half of ours). &
-- \\
\bottomrule

\end{longtable}

\footnotesize
\bibliographystyle{plainnat}
\bibliography{T12-related-work}

\end{landscape}



\end{document}